---
title: "Visualization"
author: "Natasha Woon"
date: "2026-10-01"
output: github_document
---

```{r}
library(tidyverse)
library(ggridges)

library(p8105.datasets) 
data("weather_df")

```

Now we have everything we need! 

```{r}
weather_df
```

Let's make a scatterplot! 

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

I always like the dataframe first. 

```{r}
ggp_temp_scatterplot = 
  weather_df |>
  ggplot(aes(x = tmin, y = tmax))+
  geom_point()

ggp_temp_scatterplot
```

Let's make this a bit fancier... 
```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .25) + 
  geom_smooth(se = FALSE)
```

Where you put the aesthetics matters 

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax))+
  geom_point(aes(color = name), alpha = .25) +  
  geom_smooth(se = FALSE)
```

The aesthetics are up to you 

```{r}

weather_df |>
ggplot(aes(x = tmin, y = tmax, color = name)) + 
geom_smooth(se = FALSE)

```

Show faceting 

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  facet_grid(. ~name)
```

facet_grid 

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  facet_grid(name ~ .)
```

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  facet_grid(cols = vars(name))

```

Let's look at something else. 

```{r}
weather_df |>
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
  
```

Make a plot of central park tmax v tmin only, and convert temperatures from celcius to farenheit. 

```{r}
weather_df |>
  filter(name == "CentralPark_NY") |>
  mutate(
  tmax = tmax* (9/5) + 32,
  tmin = tmin* (9/5) + 32
) |>
  ggplot(aes( x = tmin, y = tmax)) + 
  geom_point() 
```

What's a hex plot 

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
```

univariate plots 

```{r}
weather_df |>
  ggplot(aes(x = tmax, fill = name)) +
  geom_histogram(position = "dodge")
```

density plots are great!!!

```{r}
weather_df |>
  ggplot(aes(x = tmax, color = name)) +
  geom_density()
```

```{r}
weather_df |>
  ggplot(aes(x = tmax, fill = name)) +
  geom_density(alpha = .3)
```

Boxplots 

```{r}
weather_df |>
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot()
```

violin plots 

```{r}
weather_df |>
  ggplot(aes(x = name, y = tmax)) +
  geom_violin()
```

Ridge plots...
```{r}
weather_df |>
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()
```

## save some of my plots 

```{r}
ggp_weather = 
  weather_df |>
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .5) +
  facet_grid(. ~ name) 

ggp_weather

ggsave("ggp_weather.pdf", ggp_weather)
```

```{r fig.width = 12, fig.height = 12}
weather_df |>
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

